### 2025-06-21 sports-cognitive-psychology.qmd
20250621 - update REF

However, does icing the kicker work?
There is mixed evidence on icing the kicker.
Some studies find some evidence for lower percentage of iced kicks made compared to non-iced kicks [@Goldschmied2024], whereas other studies do not [e.g., @Berry2004; @GonzalezSanchez2024; @Moskowitz2011].
This suggests that, if there is such an effect, the [effect size](#sec-practicalSignificance) is likely very small, and it may better suit the team to use your timeouts in other situations.

>>>>

However, does icing the kicker work?
There is mixed evidence on icing the kicker.
Some studies find some evidence for lower percentage of iced kicks made compared to non-iced kicks [@Goldschmied2025], whereas other studies do not [e.g., @Berry2004; @GonzalezSanchez2024; @Moskowitz2011].
This suggests that, if there is such an effect, the [effect size](#sec-practicalSignificance) is likely very small, and it may better suit the team to use your timeouts in other situations.
